Compositional Verification of Concurrent C Programs with Search Structure Templates

### 2023-05-02 concurrency/CONCUR 2023/paper.tex
quick appendix edit

\section{Proofs for Sections \ref{traverse_proof_giveup}, \ref{BST_lock_insert}, and \ref{BST_giveup_insert}}
\label{sec:apd_proof}
Below are partially completed proofs of \texttt{traverse} for the give-up template (Figure \ref{proof_giveup_traverse}), as well as proofs of \texttt{insert} for the lock-coupling (Figure \ref{proof_lock_insert}) and give-up (Figure \ref{proof_giveup_insert}) templates, annotated with separation logic specifications. The complete proofs can be found in our Coq mechanization, which is mentioned in Section \ref{proof_mech} for reference.

>>>>

\section{Proof Outlines for Templates (Sections \ref{traverse_proof_lock} and \ref{traverse_proof_giveup})}
\label{sec:apd_proof}
Below are proof outlines for the \texttt{traverse} function for the give-up template (Figure \ref{proof_giveup_traverse}) as well as the \texttt{insert} function for both templates. The complete proofs can be found in our Coq mechanization (see Section \ref{proof_mech}). \wm{I should edit these if I have time.}
